Memory-aware Adaptive Scheduling of Scientific Workflows On Heterogeneous Architectures\\

### 2025-02-18 main.tex
last submitted version
author names

%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID}
%\and
%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID} }

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal2}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal-onlyvalid2}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

@@

\section{Conclusion}
\label{sec:conc}

We have formalized a scheduling problem in memory-constrained environments where tasks
may exceed the memory available on a processor and resort to communication buffers
to store and communicate data between processors. In this context, we have 
designed three memory-aware HEFT-based heuristics which account for memory
constraints when scheduling workflow tasks.

>>>>

\author{\IEEEauthorblockN{Svetlana Kulagina}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-2108-9425}
\and
\IEEEauthorblockN{Anne Benoit}
\IEEEauthorblockA{\textit{ENS Lyon, France} \\
ORCID: 0000-0003-2910-3540
}
%\textit{name of organization (of Aff.)}\\
%City, Country \\
%email address or ORCID
\and
\IEEEauthorblockN{Henning Meyerhenke}
\IEEEauthorblockA{\textit{Humboldt-Universität zu Berlin, Germany} \\
ORCID: 0000-0002-7769-726X}
}

@@

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal2}
    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, including invalid \heft schedules. }
%by algorithm by workflow size
     \label{fig:mem-usages-normal}
    \vspace{-0.15cm}
\end{figure}

\begin{figure}[tb]
    \centering
    \includegraphics[width=1\columnwidth] {images/mem-usage-normal-onlyvalid2}
    \vspace{-0.6cm}
    \caption{Memory usage on default cluster, considering only valid \heft schedules. }
    \label{fig:mem-usages-onlyvalid}
    \vspace{-0.15cm}
\end{figure}

@@

\bigskip
\section{Conclusion}
\label{sec:conc}

We have formalized a scheduling problem in memory-constrained environments where tasks
may exceed the memory available on a processor and resort to communication buffers
to store and communicate data between processors. In this context, we have 
designed three memory-aware HEFT-based heuristics that account for memory
constraints when scheduling workflow tasks.
